---
title: "Schools-Departments-from-KTH-Directory-API"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Schools-Departments-from-KTH-Directory-API}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Organizational belonging for a given KTH user account or kthid

Given an account name or "kthid", how can we look up the organizational belonging?

```{r, message=FALSE}
library(kthapi)
library(dplyr)

user <- "hoyce"
unit_codes <- kth_profile_school_dep(user)

# organizational belonging for user "hoyce"
unit_codes

# use the first two levels of the hierarchy
slug <- paste0(collapse = "/", unit_codes[1:2])

# look up the english lang description for this "slug"
unit2 <- 
  kth_school_dep() %>% 
  inner_join(tibble(slug = slug)) %>%
  select(slug, desc = `description.en`) %>%
  pull(desc)

```

Via the so called "Legacy Profile API v 1.1" we have now looked up that __`r user`__ belongs to the organizational unit __`r unit2`__.

## Level 1 and 2 organizational units

The KTH schools and departments (in this case for the first two levels of the org hierarchy) can be retrieved with `kth_school_dep()`.

In the listing we exclude the `kthid` identifier, but it exists also for organizational units.

```{r, message=FALSE}
kth_school_dep() %>% 
#  filter(is.na(`_id`)) %>%
  mutate(row = 1:nrow(.)) %>%
  select(row, slug, desc = `description.en`, website) %>%
  knitr::kable()

```
